---
title: "Procrastination"
author: "Arturo Casillas & Eric McCandless"
date: "November 26, 2017"
output:
  html_document:
    keep_md: true
---


## Introduction

Background: 

##Sources/Data

Data files: Raw and URL/Scraped

```{r, initialize}
library(knitr)
#opts_knit$set(root.dir = "~/Documents/")
#getwd()
```

```{r}
#2.
#read the data
#This assumes that CaseStudy2 is your working directory
#2.a.
procrastination<-read.csv('./Data/Procrastination.csv', header=TRUE)
```

##Additional Information

Additional information about this assessment can be found in the README file in the repository.

##Analysis/Findings

Explore Data:

Dimensions:

```{r}
#2.b.
#dimensions
dim(procrastination)
```

First Look:

```{r, results='hide'}
#general info
str(procrastination)

#Create 'catch', a vector of boolean if-numeric
catch=NA
for(i in 1:length(procrastination[1,])){catch<-c(catch, is.numeric(procrastination[,i]))}
#catch[-1]

#Numeric Summary
apply(procrastination[,catch[-1]], 2, summary)

#Character Summary
apply(procrastination[,!catch[-1]], 2, unique)
```

Clean data variable by variable:

```{r, echo=TRUE}
## Clean data by variable ###

#rename then reformat if necessary
names(procrastination)[1]<-'Age'

names(procrastination)[2]<-'Education'
levels(procrastination$Education)[match('0', levels(procrastination$Education))]<-''

names(procrastination)[6]<-'Income.Year'
#tail(sort(procrastination$Income.Year), 150)
#Consider that the incomes are buckets not values
#unique(procrastination$Income.Year)

names(procrastination)[7]<-'Current.Job'
#unique(procrastination$Current.Job)
#check for other info about 's'
#procrastination[procrastination$Current.Job == 's',]
#Set 's' to student based on employment status
levels(procrastination$Current.Job)[match('s', levels(procrastination$Current.Job))]<-'student'
levels(procrastination$Current.Job)[match('0', levels(procrastination$Current.Job))]<-''
#ouh could be oxford university hospital

names(procrastination)[8]<-'Years.Empl.'
#tail(sort(procrastination$Years.Empl.), 50)
#999 years is missing since we don't know what it means
procrastination$Years.Empl.<-ifelse(procrastination$Years.Empl. == 999, NA, procrastination$Years.Empl.)

names(procrastination)[9]<-'Months.Empl.'

names(procrastination)[10]<-'Comm.Size'
#CHeck if 8 or 0 corresponds to a category if numeric
#procrastination$Comm.Size[as.numeric(procrastination$Comm.Size) == 8]
#procrastination$Comm.Size[as.numeric(procrastination$Comm.Size) == 0]
#Change to 'Small City based on other responses
levels(procrastination$Comm.Size)[match('8', levels(procrastination$Comm.Size))]<-'Small City'
levels(procrastination$Comm.Size)[match('0', levels(procrastination$Comm.Size))]<-''

names(procrastination)[11]<-'Country'
levels(procrastination$Country)[match('0', levels(procrastination$Country))]<-''

names(procrastination)[12]<-'Marital.Stat'
levels(procrastination$Marital.Stat)[match('0', levels(procrastination$Marital.Stat))]<-''

names(procrastination)[13]<-'Sons'
levels(procrastination$Sons)[match('Male', levels(procrastination$Sons))]<-'1'
levels(procrastination$Sons)[match('Female', levels(procrastination$Sons))]<-'2'
#Convert to numeric
procrastination$Sons = as.numeric(as.character(procrastination$Sons))

names(procrastination)[14]<-'Daughters'
#procrastination$Daughters = as.numeric(procrastination$Daughters)

names(procrastination)[15]<-'XDP1'
names(procrastination)[16]<-'XDP2'
names(procrastination)[17]<-'XDP3'
names(procrastination)[18]<-'XDP4'
names(procrastination)[19]<-'XDP5'
names(procrastination)[20]<-'XAIP1'
names(procrastination)[21]<-'XAIP2'
names(procrastination)[22]<-'XAIP3'
names(procrastination)[23]<-'XAIP4'
names(procrastination)[24]<-'XAIP5'
names(procrastination)[25]<-'XAIP6'
names(procrastination)[26]<-'XAIP7'
names(procrastination)[27]<-'XAIP8'
names(procrastination)[28]<-'XAIP9'
names(procrastination)[29]<-'XAIP10'
names(procrastination)[30]<-'XAIP11'
names(procrastination)[31]<-'XAIP12'
names(procrastination)[32]<-'XAIP13'
names(procrastination)[33]<-'XAIP14'
names(procrastination)[34]<-'XAIP15'
names(procrastination)[35]<-'XGP1'
names(procrastination)[36]<-'XGP2'
names(procrastination)[37]<-'XGP3'
names(procrastination)[38]<-'XGP4'
names(procrastination)[39]<-'XGP5'
names(procrastination)[40]<-'XGP6'
names(procrastination)[41]<-'XGP7'
names(procrastination)[42]<-'XGP8'
names(procrastination)[43]<-'XGP9'
names(procrastination)[44]<-'XGP10'
names(procrastination)[45]<-'XGP11'
names(procrastination)[46]<-'XGP12'
names(procrastination)[47]<-'XGP13'
names(procrastination)[48]<-'XGP14'
names(procrastination)[49]<-'XGP15'
names(procrastination)[50]<-'XGP16'
names(procrastination)[51]<-'XGP17'
names(procrastination)[52]<-'XGP18'
names(procrastination)[53]<-'XGP19'
names(procrastination)[54]<-'XGP20'
names(procrastination)[55]<-'SWLS1'
names(procrastination)[56]<-'SWLS2'
names(procrastination)[57]<-'SWLS3'
names(procrastination)[58]<-'SWLS4'
names(procrastination)[59]<-'SWLS5'

names(procrastination)[60]<-'Self.Assess'

names(procrastination)[61]<-'Other.Assess'
#Check if '4' or '0' correspond to a categor under numeric coding
#procrastination$Other.Assess[as.numeric(procrastination$Other.Assess) == 4]
#procrastination$Other.Assess[as.numeric(procrastination$Other.Assess) == 0]
levels(procrastination$Other.Assess)[match('4', levels(procrastination$Other.Assess))]<-'no'
levels(procrastination$Other.Assess)[match('0', levels(procrastination$Other.Assess))]<-''

```

Double Check

```{r, echo=TRUE}
#Double Check
str(procrastination)

#apply(procrastination, 2, class)
catch=NA
for(i in 1:length(procrastination[1,])){catch<-c(catch, is.numeric(procrastination[,i]))}
#catch[-1]

#Numeric Summary
#apply(procrastination[,c(1,6,8:9, 14:59)], 2, summary)
apply(procrastination[,catch[-1]], 2, summary)

#Character Summary
#apply(procrastination[,-c(1,6,8:9, 14:59)], 2, unique)
apply(procrastination[,!catch[-1]], 2, unique)
```

Highlights:




###Modifications/Merges to Data

###Data Summary

##Conclusions



