---
title: "Procrastination and Human Development"
author: "Arturo Casillas & Eric McCandless (ACEM Research. Inc.)"
date: "November 26, 2017"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    #df_print: kable
    #df_print: paged
    theme: "flatly"
    keep_md: true
---


## Introduction/Background

The Better World Organization (BWO) is a socioeconomic thinktank that is interested in better understanding the relationship between procrastination and the development of countries in the world.  BWO hired ACEM Research to analyze this topic.  Specifically, BWO has asked ACEM to provide the answers to a few specific questions.  

- Top 15 Nations According to the Decisional Procrastination Scale
- Top 15 Nations According to the General Procrastination Scale
- Relationship Between Life Satisfaction and Human Development Index 
- Relationship Between Life Satisfaction and Human Development Index Levels

As part of the analysis, ACEM collected procrastination data and used the HDI from the United Nations.  MOre information about these sources is provided in the README documentation.

Additionally, initial analysis of the data needed to be conducted to assess whether there are any biases within the data set worth noting.  Analysis included:

- Descriptive Statistics - age, income, HDI, Procrastination data mean scores
- Histogram for Age 
- Histogram for Income
- Participants by Gender
- Participants by Work Status
- Participants by Occupation
- Participants by Country 
- Perceptions of Procrastination 

##Sources/Data

Data files: Raw and URL/Scraped
 * Procrastination data

```{r, initialize, warning=FALSE}
library(knitr)
library(xml2)
library(rvest)
library(ggplot2)
library(pander)
#opts_knit$set(root.dir = "~/Documents/")
#getwd()
```

Procrastination data imported and cleaned


Import the data. It has 4,264 observations and 61 variables:

```{r}
# #2.
# #read the data
# #This assumes that CaseStudy2 is your working directory
# #2.a.
procrastination<-read.csv('./Data/Procrastination.csv', header=TRUE, na.strings=c(""," ","NA"))
#read_chunk('./Analysis/procrastination_data.R')

#2.a.
#dimensions
dim(procrastination)
```

Dimensions:
 * Initial dimensions are 4264 observations and 61 variables


Clean data variable by variable:

 * Go through variables one by one
  * Rename if necessary to keep 12 characters and under
  * the '.' is used as a separator
  * Define appropriate missing values: '0' when numeric and blank when character
   * Use 2.c.iii.-iv. as examples  
   -For example, work status has a '0' instead of 'full-time' or 'retired'. This was changed to a missing value
  * Fix when factor labels are not applied correctly
   * Use 2.c.ii. as example
   - Sons has 'Male' and 'Female' instead of 1 and 2
  * Decide what to do with nonsense data
   * Use 2.c.i. as example

```{r, echo=TRUE, results='markup'}
#2.b.-2.c.

### Clean data by variable ###

#rename levels or change values

names(procrastination)[1]<-'Age'

names(procrastination)[4]<-'Education'

#names(procrastination)[5]<-'Work.Status'
levels(procrastination$Work.Status)[match('0', levels(procrastination$Work.Status))]<-NA #''

names(procrastination)[6]<-'Income.Year'
#tail(sort(procrastination$Income.Year), 150)
#Consider that the incomes are buckets not values
#unique(procrastination$Income.Year)

names(procrastination)[7]<-'Current.Job'
#unique(procrastination$Current.Job)
#check for other info about 's'
#procrastination[procrastination$Current.Job == 's',]
levels(procrastination$Current.Job)[match('na', levels(procrastination$Current.Job))]<-NA
levels(procrastination$Current.Job)[match('0', levels(procrastination$Current.Job))]<-NA

#Fix Misspellings
#ouh could be oxford university hospital was not changed
levels(procrastination$Current.Job)[match('s', levels(procrastination$Current.Job))]<-'student'
levels(procrastination$Current.Job)[match('Studey', levels(procrastination$Current.Job))]<-'student'
levels(procrastination$Current.Job)[match('psychologis', levels(procrastination$Current.Job))]<-'psychologist'
levels(procrastination$Current.Job)[match('mktg', levels(procrastination$Current.Job))]<-'Marketing'
levels(procrastination$Current.Job)[match('MD', levels(procrastination$Current.Job))]<-'Physician'
levels(procrastination$Current.Job)[match('Economy', levels(procrastination$Current.Job))]<-'Economist'
levels(procrastination$Current.Job)[match('vidoe', levels(procrastination$Current.Job))]<-'video'
levels(procrastination$Current.Job)[match(' houswife', levels(procrastination$Current.Job))]<-'Housewife'
#gsub('â???"', '', levels(procrastination$Current.Job))
levels(procrastination$Current.Job)[match('\'Utterly shiftless arts student\'... at p', levels(procrastination$Current.Job))]<-'student'
levels(procrastination$Current.Job)[match('asst', levels(procrastination$Current.Job))]<-'Assistant'

names(procrastination)[8]<-'Years.Empl.'
#tail(sort(procrastination$Years.Empl.), 50)
#999 years is missing since we don't know what it means
procrastination$Years.Empl.<-ifelse(procrastination$Years.Empl. == 999, NA, procrastination$Years.Empl.)
procrastination$Years.Empl.<-round(procrastination$Years.Empl)

names(procrastination)[9]<-'Months.Empl.'

names(procrastination)[10]<-'Comm.Size'
#CHeck if 8 or 0 corresponds to a category if numeric
#procrastination$Comm.Size[as.numeric(procrastination$Comm.Size) == 8]
#procrastination$Comm.Size[as.numeric(procrastination$Comm.Size) == 0]
#Change to 'Small City based on other responses
levels(procrastination$Comm.Size)[match('8', levels(procrastination$Comm.Size))]<-'Small City'
levels(procrastination$Comm.Size)[match('0', levels(procrastination$Comm.Size))]<-NA

names(procrastination)[11]<-'Country'
levels(procrastination$Country)[match('0', levels(procrastination$Country))]<-NA
levels(procrastination$Country)[match('', levels(procrastination$Country))]<-NA
#levels(procrastination$Country)[match(' ', levels(procrastination$Country))]<-'<NA>'

names(procrastination)[12]<-'Marital.Stat'
levels(procrastination$Marital.Stat)[match('0', levels(procrastination$Marital.Stat))]<-NA

names(procrastination)[13]<-'Sons'
levels(procrastination$Sons)[match('Male', levels(procrastination$Sons))]<-'1'
levels(procrastination$Sons)[match('Female', levels(procrastination$Sons))]<-'2'
#Convert to numeric
procrastination$Sons = as.numeric(as.character(procrastination$Sons))

names(procrastination)[14]<-'Daughters'
#procrastination$Daughters = as.numeric(procrastination$Daughters)

names(procrastination)[15]<-'XDP1'
names(procrastination)[16]<-'XDP2'
names(procrastination)[17]<-'XDP3'
names(procrastination)[18]<-'XDP4'
names(procrastination)[19]<-'XDP5'
names(procrastination)[20]<-'XAIP1'
names(procrastination)[21]<-'XAIP2'
names(procrastination)[22]<-'XAIP3'
names(procrastination)[23]<-'XAIP4'
names(procrastination)[24]<-'XAIP5'
names(procrastination)[25]<-'XAIP6'
names(procrastination)[26]<-'XAIP7'
names(procrastination)[27]<-'XAIP8'
names(procrastination)[28]<-'XAIP9'
names(procrastination)[29]<-'XAIP10'
names(procrastination)[30]<-'XAIP11'
names(procrastination)[31]<-'XAIP12'
names(procrastination)[32]<-'XAIP13'
names(procrastination)[33]<-'XAIP14'
names(procrastination)[34]<-'XAIP15'
names(procrastination)[35]<-'XGP1'
names(procrastination)[36]<-'XGP2'
names(procrastination)[37]<-'XGP3'
names(procrastination)[38]<-'XGP4'
names(procrastination)[39]<-'XGP5'
names(procrastination)[40]<-'XGP6'
names(procrastination)[41]<-'XGP7'
names(procrastination)[42]<-'XGP8'
names(procrastination)[43]<-'XGP9'
names(procrastination)[44]<-'XGP10'
names(procrastination)[45]<-'XGP11'
names(procrastination)[46]<-'XGP12'
names(procrastination)[47]<-'XGP13'
names(procrastination)[48]<-'XGP14'
names(procrastination)[49]<-'XGP15'
names(procrastination)[50]<-'XGP16'
names(procrastination)[51]<-'XGP17'
names(procrastination)[52]<-'XGP18'
names(procrastination)[53]<-'XGP19'
names(procrastination)[54]<-'XGP20'
names(procrastination)[55]<-'SWLS1'
names(procrastination)[56]<-'SWLS2'
names(procrastination)[57]<-'SWLS3'
names(procrastination)[58]<-'SWLS4'
names(procrastination)[59]<-'SWLS5'

names(procrastination)[60]<-'Self.Assess'

names(procrastination)[61]<-'Other.Assess'
#Check if '4' or '0' correspond to a categor under numeric coding
#procrastination$Other.Assess[as.numeric(procrastination$Other.Assess) == 4]
#procrastination$Other.Assess[as.numeric(procrastination$Other.Assess) == 0]
levels(procrastination$Other.Assess)[match('4', levels(procrastination$Other.Assess))]<-'no'
levels(procrastination$Other.Assess)[match('0', levels(procrastination$Other.Assess))]<-NA

```


Create Procrastination means
 * These are the mean procrastination scores per individual per category

```{r, echo=TRUE, results='markup'}
#2.e.
#Create means for category of survey questions
#First, find the indexes of the survey category in question
#Then, use apply() to find the row mean only for those categories

XGP<-grep( 'XGP', names(procrastination))
procrastination$XGP.Mean<-apply(procrastination[,XGP], 1, mean, na.rm=TRUE)

XDP<-grep( 'XDP', names(procrastination))
procrastination$XDP.Mean<-apply(procrastination[,XDP], 1, mean, na.rm=TRUE)

XAIP<-grep( 'XAIP', names(procrastination))
procrastination$XAIP.Mean<-apply(procrastination[,XAIP], 1, mean, na.rm=TRUE)

SWLS<-grep( 'SWLS', names(procrastination))
procrastination$SWLS.Mean<-apply(procrastination[,SWLS], 1, mean, na.rm=TRUE)
```

Double Check


HDI_Data Scraped and cleaned
 * Scrape HDI data and save to repository

```{r, warning=FALSE}
#Access tables on website and save and clean each of the 8 tables.

hdi_url <- ("https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index#Complete_list_of_countries")

hdi1 <- hdi_url %>%
  html() %>%
  html_nodes('table') %>%
  .[[3]] %>%
  html_table(fill=TRUE)
hdi1 <- hdi1[,-c(1:2),]
hdi1 <- hdi1[,-c(3:273),]
hdi1 <- hdi1[-c(1:3),]
colnames(hdi1) <- c("Country","HDI")
hdi1 <- hdi1[-c(27:28),]

hdi2 <- hdi_url %>%
  html() %>%
  html_nodes('table') %>%
  .[[6]] %>%
  html_table(fill=TRUE)
hdi2 <- hdi2[,-c(1:2),]
hdi2 <- hdi2[,-c(3:298),]
hdi2 <- hdi2[-c(1:3),]
colnames(hdi2) <- c("Country","HDI")
hdi2 <- hdi2[-c(29:30),]

hdi3 <- hdi_url %>%
  html() %>%
  html_nodes('table') %>%
  .[[9]] %>%
  html_table(fill=TRUE)
hdi3 <- hdi3[,-c(1:2),]
hdi3 <- hdi3[,-c(3:223),]
hdi3 <- hdi3[-c(1:3),]
colnames(hdi3) <- c("Country","HDI")
hdi3 <- hdi3[-c(21:22),]

hdi4 <- hdi_url %>%
  html() %>%
  html_nodes('table') %>%
  .[[12]] %>%
  html_table(fill=TRUE)
hdi4 <- hdi4[,-c(1:2),]
hdi4 <- hdi4[,-c(3:223),]
hdi4 <- hdi4[-c(1:3),]
colnames(hdi4) <- c("Country","HDI")
hdi4 <- hdi4[-c(22:23),]

#Bind tables and convert HDI to numeric for analysis.

hdi_total <- rbind(hdi1, hdi2, hdi3, hdi4)
hdi_total$HDI <- as.numeric(hdi_total$HDI)

#Create HDI category column and assign category to each country.

hdi_total$Development_Level <- cut(hdi_total$HDI, 
                       breaks = c(-Inf, .550, .701, .800, Inf), 
                       labels = c("Low Human Development", "Medium Human Development", "High Human Development", "Very High Human Development"),
                       right = FALSE)

#saved file "hdi.csv" to Data file in repo:
#write.csv(hdi_total, "C:/Users/emccandless/Documents/SMU/CaseStudy2/Data/hdi.csv", row.names=FALSE)

```

Merge the two datasets
 * Prepare to merge by Country / align spellings
 * Merge Procrastination and HDI_Data by Country
 * Use merged table for analysis

```{r}
############## MERGE THE TWO DATASESTS ################

#3.c.
#THis requires both 'procrasintation' and 'hdi_total' from previous codes

#Check Spellings
#sort(unique(procrastination$Country))
#sort(unique(hdi_total$Country))

#Use Spanish Spelling of COlumbia
levels(procrastination$Country)[match('Columbia', levels(procrastination$Country))]<-'Colombia'
#Use correct Spelling of Israel
levels(procrastination$Country)[match('Isreal', levels(procrastination$Country))]<-'Israel'

procrast_hdi<-merge(x=procrastination, y=hdi_total, by.x='Country', by.y='Country', all.x = TRUE)

##Check results
#summary(test$procrast_hdi)
#str(procrast_hdi)

#unique(procrast_hdi$Country[is.na(procrast_hdi$HDI)])
##No HDI for Antiqua, Bermuda, Guam, Macao, Puerto Rico, and former Yogoslavia

#Summary of missing values
#Ta<-table(procrast_hdi$Country[is.na(procrast_hdi$HDI)])
#Ta[Ta > 0]
```

##Additional Information

Additional information about this assessment can be found in the README file in the repository.

##Analysis/Findings

Removed age outliers <18 per clients request. (Q4a)

```{r, ECHO=TRUE, warning=FALSE, message=FALSE}
#Removed respondents age<18.
procrast_hdi1 <- procrast_hdi[procrast_hdi$Age>18,]
```

Descriptive Statistics - Age, Income, HDI, 4 Mean Scores (Q4b)

```{r, ECHO=TRUE, warning=FALSE, message=FALSE}
#Summary stats for key variables.
procrast_hdi2 <- apply(procrast_hdi1[,c('Age','Income.Year', 'HDI', 'XGP.Mean', 'XDP.Mean', 'XAIP.Mean', 'SWLS.Mean')], 2, function(y) summary(y, digits = 2))
kable(procrast_hdi2)
```

Histogram for Age (Q4b)

Histogram shows most respondents age 18+ from the study are under 50, however, there is a large segment age 50-60. 

```{r, ECHO=TRUE, warning=FALSE, message=FALSE}
#histogram to show distribution of respondent age.

ggplot(procrast_hdi1, aes(procrast_hdi1$Age)) +
  geom_histogram() +
  xlab("Age") 
```

Histogram for Income (Q4b)

Histogram shows most respondents from the study have income below 100K, however, there is a large segment with income of 150K. 

```{r, ECHO=TRUE, warning=FALSE, message=FALSE}
#histogram to show distribution of respondent income.
ggplot(procrast_hdi1, aes(procrast_hdi1$Income.Year)) +
  geom_histogram() + theme_minimal() +
  xlab("Income") 
```

```{r}

## We find this more useful than table()
## A different analyst can use table() or a different function ahead
EMTABLE<-function(df, var1 = 'Variable', digits = 1){
  
 # df<-procrast_hdi1$Gender
 # digits = 1
 # var1 = 'Variable'

  procrast_hdi10 <- table(df)
  #Convert to data.frame
  procrast_hdi11 <- data.frame(cbind(procrast_hdi10, prop.table(procrast_hdi10)))
  #Tidy Count and Percentage
  names(procrast_hdi11) <- c("Count", "Percentage")
  procrast_hdi11$Percentage <- round(procrast_hdi11$Percentage * 100, digits=digits)
  #Descending order
  procrast_hdi11 <- procrast_hdi11[order(-procrast_hdi11$Percentage), ,drop = FALSE]
  #Row.Names as column
  procrast_hdi12 <- cbind(rownames(procrast_hdi11), procrast_hdi11)
  names(procrast_hdi12)[1] = var1
  rownames(procrast_hdi12) <- 1:nrow(procrast_hdi12)  
  
  #This outputs this table to our preferred format
  return(procrast_hdi12)

}
```

Participants by Gender (Q4c)

Counts of how many participants there were by gender in decending order.  There were 70 observations without a gender value.  These observations were removed from the list prior to creating the table.


```{r}
#4.c.
## These are frequency tables for three key variables

#First, table for gender
Gend.Table<-EMTABLE(procrast_hdi1$Gender, digits=1, var1 = 'Gender')
kable(Gend.Table)
```

Participants by Work Status (Q4c)

Counts of how many participants there were by work status in decending order.  There were 113 observations without a work status value.  These observations were removed from the list prior to creating the table.

```{r}
#4.c.
#Then, table for work status
WorkStat.Table<-EMTABLE(procrast_hdi1$Work.Status, digits=1, var1 = 'Work Status')
kable(WorkStat.Table)
```

Participants by Occupation (Q4c)

Shown here are the twenty largest counts of how many participants there were by current occupation in decending order of frequency.  There were 2654 observations without an occupation value.  These observations were removed from the list prior to creating the table. Given that this was a write in response, there are a large number of unique responses. A full list of all of responses can be found in the repository.

```{r}
#4.c.
#Then, table for Job Table
JobTable<-EMTABLE(procrast_hdi1$Current.Job, digits=1, var1 = 'Current Occupation')
kable(JobTable[1:20,])

####EXPORT
#write.csv(JobTable, file='~/Data/Current_Job_Freq.csv')
```




???????????????????????????????????????????????????????

Participants by Country (Q4d)

Counts of how many participants there were by country in decending order.  There were 231 observations without a country name.  These observations were removed from the list prior to creating the table.

```{r}
#4.d.
#Top 15 countries among our respondents
Country.Table<-EMTABLE(procrast_hdi1$Country, digits=2, var1 = 'Country')
kable(Country.Table)
#Note: NA or no response accounted for 231 participants, putting it in 4th place
```

Perceptions of Procrastination (Q4e)

Data show that 2,841 respondents' perception of whether or not they are a procrastinator matched what others think.  This equates to 69% of the respondent base.

```{r}
#4.e.
#
Match.Assess <- data.frame('Match.Assess'<-paste(procrast_hdi1$Self.Assess , procrast_hdi1$Other.Assess, sep = "|"))
MatchTable<-EMTABLE(Match.Assess, digits=1, var1 = 'Assessment: Self | Others')
kable(MatchTable)
```

Top 15 Nations According to the Decisional Procrastination Scale - DP (Q5b)

```{r, ECHO=TRUE, warning=FALSE, message=FALSE, fig.width=15, fig.height=10}
#table that summarizes DP means by country.
DP_Mean <- procrast_hdi1[,c("Country", "XDP.Mean")]
DP_Mean <- aggregate(DP_Mean[, c("XDP.Mean")], list(DP_Mean$Country), mean)
colnames(DP_Mean) <- c("Country", "XDP.Mean")

#second table that shows development level by country.
DP_Mean1 <- procrast_hdi1[,c("Country","Development_Level")]
DP_Mean1 <- unique(DP_Mean1)

#merging 2 tables to get DP and development category together in df.
DP_Meanfinal <- merge(DP_Mean, DP_Mean1, by=c("Country"))
DP_Meanfinal = DP_Meanfinal[-1,]
DP_Meanfinal <- DP_Meanfinal[order(-DP_Meanfinal$XDP.Mean), ,drop = FALSE]
DP_Meanfinal <- head(DP_Meanfinal,15)
DP_Meanfinal$XDP.Mean <- round(DP_Meanfinal$XDP.Mean, digits=1)
DP_Meanfinal$Development_Level <- as.character(DP_Meanfinal$Development_Level)
DP_Meanfinal$Development_Level[is.na(DP_Meanfinal$Development_Level)] <- "No Development Level Reported"


#creating bar plot.
ggplot(DP_Meanfinal, aes(x=reorder(Country,XDP.Mean),y=XDP.Mean)) +
  geom_bar(stat="identity", aes(fill=Development_Level)) +
  theme_minimal() + 
  ggtitle("Top 15 Nations in Average DP Procrastination Scores") +
  theme(plot.title = element_text(hjust = 0.5, size=20), axis.text=element_text(size=15), axis.title=element_text(size=20), legend.title=element_text(size=20), legend.text=element_text(size=15)) +
  xlab("Country of Residence") +
  ylab("Mean DP Response") +
  geom_text(aes(label = XDP.Mean), hjust=-.25, size=5) +
  scale_fill_manual(values = c('#39ac73', '#c6ecd9', '#206040')) +  
  coord_flip()

```

Top 15 Nations According to the General Procrastination Scale - GP (Q5c)

Data show that 9 countries show up in the top 15 in both the DP and GP scale.  The countries are Slovania, Taiwan, Puerto Rico, Qatar, Panama, Sri Lanka, Austria, Ecuador, and Uruguay.

```{r, ECHO=TRUE, warning=FALSE, message=FALSE, fig.width=15, fig.height=10}
#merging 2 tables to get GP and development category together in df.
GP_Mean <- procrast_hdi1[,c("Country", "XGP.Mean")]
GP_Mean <- aggregate(GP_Mean[, c("XGP.Mean")], list(GP_Mean$Country), mean)
colnames(GP_Mean) <- c("Country", "XGP.Mean")
#second table that shows development level by country.
GP_Mean1 <- procrast_hdi1[,c("Country","Development_Level")]
GP_Mean1 <- unique(GP_Mean1)
#merging 2 tables to get DP and development category together in df.
GP_Meanfinal <- merge(GP_Mean, GP_Mean1, by=c("Country"))
GP_Meanfinal = GP_Meanfinal[-1,]
GP_Meanfinal <- GP_Meanfinal[order(-GP_Meanfinal$XGP.Mean), ,drop = FALSE]
GP_Meanfinal <- head(GP_Meanfinal,15)
GP_Meanfinal$XGP.Mean <- round(GP_Meanfinal$XGP.Mean, digits=1)
GP_Meanfinal$Development_Level <- as.character(GP_Meanfinal$Development_Level)
GP_Meanfinal$Development_Level[is.na(GP_Meanfinal$Development_Level)] <- "No Development Level Reported"
#creating bar plot.
ggplot(GP_Meanfinal, aes(x=reorder(Country,XGP.Mean),y=XGP.Mean)) +
  geom_bar(stat="identity", aes(fill=Development_Level)) +
  theme_minimal() +
  ggtitle("Top 15 Nations in Average GP Procrastination Scores") +
  theme(plot.title = element_text(hjust = 0.5, size=20), axis.text=element_text(size=15), axis.title=element_text(size=20), legend.title=element_text(size=20), legend.text=element_text(size=15)) +
  xlab("Country of Residence") +
  ylab("Mean GP Response") +
  geom_text(aes(label = XGP.Mean), hjust=-.25, size=5) +
  #scale_fill_manual(values = c('royalblue3','steelblue1', 'lightcyan', 'darkblue')) +  
  scale_fill_manual(values = c('#0047b3','#4da6ff', '#e6f2ff', '#001a4d')) + 
  #scale_fill_brewer(palette="Dark2") +
  coord_flip()

```

Relationship Between Age and Income (Q5d)

According to the scatterplot below, there appears to be a relationship between age and yearly income. The relationship appers to be stronger for Males.

```{r, ECHO=TRUE, warning=FALSE, message=FALSE, fig.width=15, fig.height=10}
library(plyr)
#get frequencies
q5d<-count(procrast_hdi1, c("Age", "Income.Year", "Gender"))
#str(q5d)

#merge frequencies to procrast_hdi1 to read into ggplot
freqAIG<-merge(procrast_hdi1, q5d, by=c("Age", "Income.Year", "Gender"), all.x = TRUE)
#dim(freqAIG)

#creating scatterplot.
ggplot(na.omit(procrast_hdi1), aes(x=Age, y=Income.Year, color=Gender, fill=Gender, shape=Gender)) + 
  theme_minimal() +
  geom_point() + geom_smooth(method=lm) +  #Make scatterplot and add linea
  stat_sum() + scale_size(guide = "none") + #size by counts
  scale_shape_manual(values=c(19, 18, 20))+
  scale_colour_hue(l=50) +
  scale_fill_manual(values = c('orange','lightblue2')) +                 
  #scale_size_manual(values=4)+
  ggtitle("Age Versus Income") +
  theme(plot.title = element_text(hjust = 0.5, size=20), axis.text=element_text(size=15), axis.title=element_text(size=20), legend.title=element_text(size=20), legend.text=element_text(size=20)) +
  xlab("Age") +
  ylab("Income") 
```

The sizes of the points are larger for larger frequencies. 


Relationship Between Life Satisfaction and HDI (Q5e)

According to the scatterplot, there appears to be no relationship between mean Life Satsisfaciton and HDI. There appears to be little variability in the HDI values, in that most of our respondents live inc countries with an HDI of around 0.90. Thus, it becomes difficult to test general differences in Life Satisfaction vs HDI 

```{r, ECHO=TRUE, warning=FALSE, message=FALSE, fig.width=15, fig.height=10}

#creating scatterplot.
ggplot(procrast_hdi1, aes(x=SWLS.Mean, y=HDI)) + theme_minimal() +
  geom_point() + geom_smooth(method=lm) +
  scale_colour_hue(l=50)+
  ggtitle("Life Satisfaction Versus HDI") +
  theme(plot.title = element_text(hjust = 0.5, size=20), axis.text=element_text(size=15), axis.title=element_text(size=20), legend.title=element_text(size=20), legend.text=element_text(size=20)) +
  xlab("Life Satisfaction") +
  ylab("HDI") 
```

Relationship Between Life Satisfaction and HDI (Development Level) (Q5e)

?????????????????????????????????????????????????

```{r, ECHO=TRUE, warning=FALSE, message=FALSE, fig.width=15, fig.height=10}

HDI.level.table<-aggregate(procrast_hdi1$SWLS.Mean, by=list(procrast_hdi1$Development_Level), FUN=mean)
names(HDI.level.table)<-c("Development_Level", 'SWLS.Mean')

#creating scatterplot.
  ggplot(HDI.level.table, aes(y=SWLS.Mean, x=Development_Level, fill=Development_Level)) + theme_minimal() +
  geom_bar(stat="identity") + 
  scale_fill_brewer(palette="YlOrRd") #+
#  scale_colour_hue(l=50) 
#   ggtitle("Life Satisfaction Versus HDI") +
#   theme(plot.title = element_text(hjust = 0.5, size=20), axis.text=element_text(size=15), axis.title=element_text(size=20), legend.title=element_text(size=20), legend.text=element_text(size=20)) +
#   xlab("Life Satisfaction") +
#   ylab("HDI Development Level") 
```

Data Output

The finalized HDI table can be found in the Data folder in repository (hdi.csv). (Q6a)

The Tidied version of the original data and merged HDI data... (Q6b)

Dataset (or two) that shows the Top 15 nations... (Q6c)

d All output should be in plain English or translated in the Codebook. (Q6d)


Highlights:




###Modifications/Merges to Data

###Data Summary

##Conclusions

????? Mention biases in procrastination data set.
????? Conclusions about procrastination related to country



